\tool: Revisiting BadUSB with Type-C

### 2021-03-04 WOOT/Files/experiment.tex
delete GoodUSB from experiment

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
target device.  During this experiment, \tool disguised itself as a normal
keyboard and a home-brewed version of GoodUSB~\cite{tian2015defending} is
deployed to test the defense-bypassing. We have tried to deploy the original
GoodUSB on the target device; as the GoodUSB is proposed in 2015, the code is
outdated and cannot be executed at target device; so we have to home-brew a similar
defense mechanism based on its paper~\cite{tian2015defending}.  In the
beginning, our home-brewed version of GoodUSB asked the victim to manually complete
a CAPTCHA to authorize the new USB device, a.k.a our \tool.
%But at this time,
%by the design of GoodUSB,
%\fengwei{The following sentence is hard to
%understand.}\hongyi{Fixed, removed redundant description}
However, our attack can enter keystrokes to complete the
CAPTCHA with the video stream by \tool. Up
to this point, the bypass of defense like GoodUSB is completed and our \tool
becomes a trusted device. Next, our
\tool works similar to the original BadUSB, inserting keystrokes to perform
arbitrary execution on the laptop. We tested three scripts, ranging from
reverse shell backdoor to malware payload execution, all of which resulting in
success. With this experiment, we have demonstrated the defense-bypassing is successful
using \tool.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

>>>>

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
target device. \hongyi{TODO: FIXING} We tested three scripts, ranging from
reverse shell backdoor to malware payload execution, all of which resulting in
success. With this experiment, we have demonstrated the defense-bypassing is successful
using \tool.
%This also warned us that we need more thorough defense against such BadUSB
%attack.
